Virtualisierung eines Echtzeit-Betriebssystems zur Steuerung eines Roboters mit Schwerpunkt auf die Einhaltung der Echtzeit

### 2024-03-21 Masterarbeit_Robotik_Pamuk.tex
kvm_exit plot
add xenomai to .tex

The main objective of this work is to create a real-time robot control platform that integrates Salamander OS, Xenomai, QEMU and PCV-521 in the Yocto environment. By combining these technologies, a platform is to be created that provides real-time functions and efficient communication systems. This integration is expected to lead to a significant improvement in the response time and reliability of robot applications.

@@

\clearpage 
\chapter{Hauptteil}
\clearpage
\chapter{Results}
\clearpage
\chapter{Discussion}
\clearpage
\chapter{Summary and Outlook}
I am using \cite{blackadarHistoricalReviewCauses2016} for citing.

>>>>

The main objective of this work is to create a real-time robot control platform that integrates Salamander OS, Xenomai, QEMU and PCV-521 in the Yocto environment.

This integration is expected to lead to a significant improvement in the response time and reliability of robot applications.

@@

\clearpage 
\chapter{Salamander 4}
Salamander 4 ist das proprietäre Betriebssystem. Es basiert auf der Linux-Architektur und integriert zusätzlich Xenomai, eine Echtzeit-Entwicklungsumgebung \cite{XenomaiXenomai}.

Durch die Kombination dieser Technologien bietet Salamander OS sowohl die Flexibilität und Offenheit von Linux als auch die Echtzeitfähigkeiten von Xenomai, was es zu einer idealen Lösung für unsere spezifischen Anforderungen macht.”

\clearpage
\chapter{Results}
\clearpage
\chapter{Discussion}
\clearpage
\chapter{Summary and Outlook}
I am using \cite{blackadarHistoricalReviewCauses2016} for citing.
